State of the Practice for Lattice Boltzmann Method Software

### 2023-07-29 StateOfPractice/Papers/LatticeBoltz_SOP/LatticeBoltz_SOP.tex
Removed confusing comma from abstract

    We analyze the state of software development practice for Lattice Boltzmann
    solvers by quantitatively and qualitatively measuring and comparing 24
    software packages for 10 software qualities (installability, correctness/
    verifiability, reliability, robustness, usability, maintainability,
    reusability, understandability, visibility/transparency and
    reproducibility). Our reproducible analysis method employs a measurement
    template (containing 108 measures that are manually and automatically
    extracted from the project repository) and developer interviews (consisting
    of 20 questions). After measuring, we rank the software using the Analytic
    Hierarchy Process (AHP). Our ranking is roughly consistent with GitHub stars
    ranking, suggesting at least a partial correlation between the use of best
    practices and popularity. We find the state of the practice to be healthy,
    with 67\% of the measured packages ranking in the top two for at least two
    qualities, the majority of LBM generated artifacts corresponding to general
    recommendations from research software developers, common use of version
    control (67\% of packages) and the adoption of a quasi-agile development
    process.  Areas of best practice to potentially improve include adoption of
    continuous integration, API documentation and enforcement of programming
    style guides.  We interviewed four developers to gain insight into their
    current pain points. Identified challenges include lack of development time,
    lack of funding, and difficulty with ensuring correctness.  Developers are
    addressing these pain points by designing for change, circumventing the
    oracle problem and prioritizing documentation and usability. For future
    improvements we suggest the following: employing linters, conducting
    rigorous peer reviews, writing and submitting more papers on software,
    growing the number of contributors by following current recommendations for
    open source projects, and augmenting the theory manuals to include more
    requirements specification relevant information.

>>>>

    We analyze the state of software development practice for Lattice Boltzmann
    solvers by quantitatively and qualitatively measuring and comparing 24
    software packages for 10 software qualities (installability, correctness/
    verifiability, reliability, robustness, usability, maintainability,
    reusability, understandability, visibility/transparency and
    reproducibility). Our reproducible analysis method employs a measurement
    template (containing 108 measures that are manually and automatically
    extracted from the project repository) and developer interviews (consisting
    of 20 questions). After measuring, we rank the software using the Analytic
    Hierarchy Process (AHP). Our ranking is roughly consistent with GitHub stars
    ranking, suggesting at least a partial correlation between the use of best
    practices and popularity. We find the state of the practice to be healthy
    with 67\% of the measured packages ranking in the top two for at least two
    qualities, the majority of LBM generated artifacts corresponding to general
    recommendations from research software developers, common use of version
    control (67\% of packages) and the adoption of a quasi-agile development
    process.  Areas of best practice to potentially improve include adoption of
    continuous integration, API documentation and enforcement of programming
    style guides.  We interviewed four developers to gain insight into their
    current pain points. Identified challenges include lack of development time,
    lack of funding, and difficulty with ensuring correctness.  Developers are
    addressing these pain points by designing for change, circumventing the
    oracle problem and prioritizing documentation and usability. For future
    improvements we suggest the following: employing linters, conducting
    rigorous peer reviews, writing and submitting more papers on software,
    growing the number of contributors by following current recommendations for
    open source projects, and augmenting the theory manuals to include more
    requirements specification relevant information.
